%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
%\advance\leftskip by 1.5 %em
%\advance\itemindent by -1%.5 em
\addtocontents{toc}{\protect\vspace{1ex}}
\addcontentsline{toc}{chapter}{\bf\hspace{0.47cm} Refer\^encias Bibliogr\'aficas}
\addtocontents{toc}{\protect\vspace{1ex}}


% Referências

\bibitem{goswani03} GOSWANI, D. Optical pulse shaping approaches to coherent control. {\it PHYSICS REPORTS}, v.374, p.385-481 (2003).

\bibitem{science93} WARREN, W.; RABITZ, H.; DAHLEH, M. Coherent control of quantum dynamics: the dream is alive. {\it SCIENCE}, v.259, p.1581-1589 (1993).

\bibitem{rabitz00} RABITZ, H. {\it et al.} Whither the future of controlling quantum phenomena. {\it SCIENCE}, v.288, p.824-828 (2000).

\bibitem{rabitz_zhu00}  RABITZ, H.; ZHU, W. Optimal control of molecular motion: design, implementation, and inversion. {\it ACCOUNTS OF CHEMICAL RESEARCH}, v.33, p.572-578 (2000).

\bibitem{kawashima95} KAWASHIMA H.; WEFERS M. M.; NELSON K. A. Femtosecond pulse shaping, multiple-pulse spectroscopy, and optical control. {\it ANNUAL REVIEW OF PHYSICAL CHEMISTRY}, v.46, p.627-656 (1995).

\bibitem{assion98} ASSION A. {\it et al.} Control of chemical reactions by feedback-optimized phase-shaped femtosecond laser pulses. {\it SCIENCE}, v.282, p.919-922 (1998).

\bibitem{silberberg09} SILBERBERG Y.. Quantum Coherent Control for Nonlinear Spectroscopy and Microscopy. {\it ANNUAL REVIEW OF PHYSICAL CHEMISTRY}, v.60, p.277-292 (2009).

\bibitem{vivie-riedle01} DE VIVIE-RIEDLE R.; KURTZ L.; HOFMANN A. Coherent control for ultrafast photochemical reactions. {\it PURE AND APPLIED CHEMISTRY}, v.73, p.525-528 (2001).

\bibitem{gordon97} GORDON R. J.; RICE S. A. Active control of the dynamics of atoms and molecules. {\it ANNUAL REVIEW OF PHYSICAL CHEMISTRY}, v.48, p.601-641, (1997).



\end{thebibliography}





